---
output:
  html_document
---
```{r setup, include=FALSE}
if (length(commandArgs(trailingOnly=TRUE)) > 0) {
  args <- commandArgs(trailingOnly=TRUE)
}
validators <- read.csv(args[1])
library(ggplot2)
library(treemapify)
library(dplyr)
```
# Marinade Scoring Report `r args[2]`
## Overview
```{r, echo=FALSE}
library(knitr)
df <- data.frame(type = c("Performance Based Stake", "MNDE voting", "mSOL directing", "", "**Total Stake**"),
                 stake = c(
                   sum(validators$target_stake_algo),
                   sum(validators$target_stake_mnde),
                   sum(validators$target_stake_msol),
                   "",
                   sum(validators$target_stake)
                 ),
                 validators = c(
                   sum(validators$target_stake_algo > 0),
                   sum(validators$target_stake_mnde > 0),
                   sum(validators$target_stake_msol > 0),
                   "",
                   sum(validators$target_stake > 0)
                 ),
                 perf = c(
                   round(sum(validators$avg_adjusted_credits * validators$target_stake_algo) / sum(validators$target_stake_algo)),
                   round(sum(validators$avg_adjusted_credits * validators$target_stake_mnde) / sum(validators$target_stake_mnde)),
                   round(sum(validators$avg_adjusted_credits * validators$target_stake_msol) / sum(validators$target_stake_msol)),
                   "",
                   round(sum(validators$avg_adjusted_credits * validators$target_stake) / sum(validators$target_stake))
                 )
)
kable(df, col.names = c("Stake type", "Stake amount", "Validators", "Stake-weighted, commission-adjusted voting performance"))
```

The plot below shows the voting performance of all validators in Solana. Purple lines denote validators who are supposed to receive any stake from Marinade.

```{r, echo=FALSE, fig.align="center", fig.width = 10}
df <- validators[validators$avg_adjusted_credits > 0,]
df$x <- factor(df$vote_account, levels = df$vote_account[order(-df$avg_adjusted_credits)])

df$fill <- ifelse(df$target_stake > 0, "purple", "gray")


ggplot(df, aes(x=df$x, y=df$avg_adjusted_credits)) +
  geom_bar(stat = "identity", width = 1, colour = "transparent", fill = df$fill) +
  ylim(0, 432000) +
  labs(title="Validators' voting performance", x = "Validators", y = "Average commission adjusted vote credits") +
  scale_x_discrete(labels = NULL) +
  theme_minimal()
```

The plots below show validators and their scores as calculated by the Delegation Strategy. The plot (A) shows which validators were picked by the performance-based scoring formula. The plot (B) shows which validators were picked by MNDE votes.

```{r, echo=FALSE, fig.align="center", fig.width = 10}
df <- validators
df$x <- factor(df$vote_account, levels = df$vote_account[order(-df$score)])

df$fill_algo <- ifelse(df$target_stake_algo > 0, "purple", "gray")

df$fill_mnde <- ifelse(df$target_stake_mnde > 0, "purple", "gray")


plot1 <- ggplot(df, aes(x=x, y=score)) +
  geom_bar(stat = "identity", width = 1, colour = "transparent", fill = df$fill_algo) +
  ylim(0, 1) +
  labs(title="Validators picked by their performance", x = "Validators", y = "Score", tag = "A") +
  scale_x_discrete(labels = NULL) +
  theme_minimal()

plot2 <- ggplot(df, aes(x=x, y=score)) +
  geom_bar(stat = "identity", width = 1, colour = "transparent", fill = df$fill_mnde) +
  ylim(0, 1) +
  labs(title="MNDE voted validators", x = "Validators", y = "Score", tag = "B") +
  scale_x_discrete(labels = NULL) +
  theme_minimal()

gridExtra::grid.arrange(plot1, plot2, ncol=2)
```

## Stake distribution in data centers
The plots in this section show how Marinade plans to distribute the stake between different data centers and how stake is distributed in the whole Solana cluster.

```{r, echo=FALSE, fig.align="center", fig.width = 10}
df <- validators %>% 
  group_by(dc_aso) %>% 
  summarize(stake = sum(target_stake_algo))
df$pct <- round(df$stake / sum(df$stake) * 100, digits = 2)

# Create a treemap
ggplot(df, aes(
                area = stake,
                fill = dc_aso,
                label = paste(dc_aso, stake, paste(pct, "%"), sep = "\n"))
       ) +
  geom_treemap() +
  geom_treemap_text(colour = "white",
                    place = "centre",
                    size = 15) +
  theme(legend.position = "none") +
  labs(title = "Performance-based part of Marinade stake by ASO")
```


```{r, echo=FALSE, fig.align="center", fig.width = 10}
df <- validators %>% 
  group_by(dc_aso) %>% 
  summarize(stake = sum(target_stake))
df$pct <- round(df$stake / sum(df$stake) * 100, digits = 2)

# Create a treemap
ggplot(df, aes(
                area = stake,
                fill = dc_aso,
                label = paste(dc_aso, stake, paste(pct, "%"), sep = "\n"))
       ) +
  geom_treemap() +
  geom_treemap_text(colour = "white",
                    place = "centre",
                    size = 15) +
  theme(legend.position = "none") +
  labs(title = "Total planned Marinade stake by ASO")
```


```{r, echo=FALSE, fig.align="center", fig.width = 10}
df <- validators %>% 
  group_by(dc_aso) %>% 
  summarize(stake = sum(avg_stake))
df$pct <- round(df$stake / sum(df$stake) * 100, digits = 2)

# Create a treemap
ggplot(df, aes(
                area = stake,
                fill = dc_aso,
                label = paste(dc_aso, stake, paste(pct, "%"), sep = "\n"))
       ) +
  geom_treemap() +
  geom_treemap_text(colour = "white",
                    place = "centre",
                    size = 15) +
  theme(legend.position = "none") +
  labs(title = "Solana stake distribution by ASO")
```
